Spreading of a Facebook Application

### 2011-04-15 paper.tex
checked abstract to methodology

@@

\title{Distribution of a Facebook application}

@@

\begin{abstract}
%% Text of abstract, 150 - 350 words
% The outcome was students' perceptions of preparedness.
This paper investigates, how a small Facebook application 
distributes among friends. A graph is created which represents users, who
installed the application, as nodes and friendship between them as
edges. In addition, metrics are calculated to determine, which
parameters  make users likely to invite their friends to
participate.

The application itself is a quiz which asks people 5
questions, randomly selected from a pool of 20 questions, 
about dentistry health facts. After the quiz, participants
get to know if they had a higher score than their friends and who of their
friends answered the questions they got correctly.

Results show users, who yield a high score in the quiz,
more likely to invent other users than users, who got a worse
score. In addition, the number of friends did not mark users to be
relevant for spreading the app. Indeed, people who had less friends
were much more likely to spread the application.
\end{abstract}

@@

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
Facebook, Social Networking, data mining, social graph
\end{keyword}

@@

\section{Introduction}
\label{sec:introduction}
Founded in 2004, Facebook\footnote{www.facebook.com} has
become a social network currently used by more than 600 million people
all over the world\cite{facebook500}. Since 2007, Facebook provides an API allowing
third party developers to embed their own applications into
Facebook\footnote{http://developers.facebook.com/blog/archive}.
Subsequent to the F8 conference in April, 2010, Facebook simplified
access to its social graph via Open Graph Protocol \cite{facebookStats} and allowed
for integration of external websites. Until October, 2009,
over 350 000 apps had been seen on Facebook \cite{facebookBlog}.
Due to current statistics, people install about 20 million apps per day. In addition, ten thousand new
websites integrate with Facebook every day. \cite{facebookStats}

Due to integration in Facebook's social graph, third party
applications spare user authentication procedures and can access
private user information as well. These information can include basic
information and friend lists, but also interests and further data
specified by an access token  \footnote{http://developers.facebook.com/docs/authentication/}.
As the data provided by Facebook, and collected by analyzing user
behaviour on an application, represent a lot of social information, it
seems obvious, that these data also allow for studying social groups.

This paper investigates the distribution process of a quiz on Facebook
by analysing which parameters make users likely to distribute the application
and which parameters do not.

In the first section, background information
about how applications can be integrated with Facebook are
given. Then, the methodology is described in section \ref{sec:method},
including the quiz, as well as the 
proceedings used for data collection and evaluation. In section
\ref{sec:results}, the results are detailed, and in section
\ref{sec:discussion} and \ref{sec:outlook}, they are discussed and an
outlook is given for further research.

\section{Background}
\label{sec:background}
This section describes the social graph concept, how applications can be integrated with
Facebook, how authentication and authorisation is done, and in which
format data from the social graph can be obtained.

\subsection{Social Graph}
\label{sec:social-graph}
The \textit{social graph} is at Facebook's core. It represents
connections between people and things they care about
\cite{facebookDev}. In April, 2010, Facebook included access to the
social graph via the Open Graph Protocol, which advanced integration of
external websites into the social graph \cite{facebookDev2}. These websites can make use of
social plugins such as \textit{Like Buttons} or \textit{Comment Boxes} \cite{facebookDev2}
and for this reason, the social graph contains not only connections between
people on Facebook (friend relations), but also between 
entities such as applications, movie entries on external websites,
news articles, and much more. As this allows
people to identify friends on external websites and receive
information about their friends' attitude towards anything their
friends have visited and commented before, one can say
that Facebook's social graph makes the Internet social.

The Graph API is one of Facebook's core concepts and presents a consistent
view of the social graph. Every object has an unique ID and its
properties can be accessed by requesting the appropriate URL:
\url{https://graph.facebook.com/ID}. Listing \ref{list:kbecker} shows
the author's public user node on Facebook's social graph. which is
returned as a \ac{json}-object\footnote{http://www.json.org}.

@@

In order to get access not only to public, but also to private
information, an access token has to be included in the Graph API
request. To get this token, the accessing entity must be
authorized and authenticated to do so. How this can be achieved is
discussed in section \ref{sec:auth-auth}. If one tries to access
non-public information such as the author's list of friends, an error
in terms of a missing access token is returned. An example is given in
listing \ref{list:kbeckerfriends}.

@@

Facebook provides several features to support the development
process. \ac{sdks} exist for popular programming languages and provide
sets of pre-defined functions for communication with Facebook. For
instance, they include the O-Auth 2.0 dialog which is described in
section \ref{sec:auth-auth}. In
addition, Facebook grants observation of its own development process by
making its raodmap public, and by showing its buglist. In addition, a
testserver exists to help developers to analyze if their application
is going to run with planned features from Facebook. 
Facebook provides an \textit{insights}-feature which makes
statistics about the applications available. \cite{oreilly}.

@@

\section{Methodology}
\label{sec:method}
In this section, the quiz is described as well as its
implementation. Then, it is explained how data are collected for
further analysis and how they can be evaluated.

\subsection{The Quiz}
\label{sec:quiz}
The quiz contains questions in German about dentistry health facts. Participants are asked 5
questions taken from a pool of 20 questions. Each question has 4
possible answers. Multiple selection is possible, but at least one
answer is correct. A question is answered correctly, if each correct
and no incorrect answer have been selected. Figure \ref{fig:quiz}
shows how the quiz looks like.

The quiz is competitive. After the quiz is completed, user are told
how good they were in comparison to other participants and to their
friends. As shown in figure \ref{fig:solution}, for each question the
correct solution is given. A user can also invite friends to
participate by clicking on the appropriate image. This is demonstrated in
figure \ref{fig:invite}.

\subsection{Implementation}
\label{sec:implementation}
The quiz-application detailed in the last section makes use of
Facebook's php-\ac{sdk} and JavaScript-\ac{sdk}. It requires
permissions for \textit{user$\_$birthday} and
\textit{publish$\_$stream}.
Data used by the quiz are stored in a MySQL-database, and php scripts
handle the application flow. \textit{index.php} maintains calls of
scripts printing the quiz (\textit{quiz.php}, \textit{question.php}), and displaying
the correct solution as well as the opportunity to invite friends
after completion of the quiz
(\textit{quizResult.php}). \textit{library.php} contains all the
functions needed.

\subsubsection{Database schema}
\label{sec:database-schema}
The database queries are performed with PHP
pear\footnote{http://pear.php.net/}-package. The following tables exist:
\begin{itemize}
\item \textbf{User} - entries are created for each user who participates as
well as for each of a user's friends. A flag details if user
participated or not.
\item \textbf{Friends} - creates entries for each friendship found in
users' friend lists.
\item \textbf{Questions} - contains the questions of the quiz.
\item \textbf{Answers} - contains the possible answers and a flag to mark them
as correct or false.
\item \textbf{GivenAnswers} - stores each answer given by a user.
\item \textbf{UserScore} - stores the score user had in the quiz.
\item \textbf{CorrectAnsweredQuestions} - stores which questions were correct
answered by which user, and which were not.
\end{itemize}

\subsubsection{Application flow}
\label{sec:application-flow}
When a user enters, the \textit{OAuth Dialog} is started. Then, the user data
including gender, birthday, name, Facebook-ID are stored together with
a timestamp, and column \textit{has-used-app} is set to 1. In
addition, each user's friends are also stored and column
\textit{has-used-app} is set to 0. Then, friendships are stored in the
table \textit{friends}. Next, the quiz is created by randomly choosing
five questions from the questions table and requiring the answers. To
make the questions more attractive, the name of an image convenient to
the questions topic is also stored in the questions table, and this
image is placed on the left side of each question. Since multiple
selection is possible, before the answers, which are also queried from
the MySQL database, checkboxes are placed before each answer.

As soon as a user completed the quiz, evaluation starts by checking
which questions were answered correctly and by computing the final
score. Due to multiple selection, user answers are stored in
an multidimensional array and compared with another multidimensional
array containing the correct solution and created from the database.
The given answers are then stored, and in addition, in another table
(\textit{correctAnsweredQuestions)}
it is only stored which questions were correct and incorrect answered.
Some user join the quiz multiple times, and for this reason, each
score they had is stored in a score table. The user table is also
changed by entering or updating the average score, computed from each all the scores stored
in the score table. Then, by using the Java Script \ac{sdk}, the user
get the option to post the results onto their Facebook wall.

In order to make the whole thing challenging, it
is then computed how high the user's score is compared to the friends
and to all the other users. 
In addition, the correct solutions are given, and if a user knew the
right answer, a green check is placed left to the question. Otherwise,
a red cross is displayed at the same place. At least, the table with
the friendships and table \textit{correctAnsweredQuestions} are used
to identify friends  which answered the question correctly. Images of
them are placed beyond each question's solution together with the
information that those friends knew the right solution. 
In the end, users get the chance to invite friends to the app to
challenge them. For this reason, each friend's picture is added and
user can click at them. On click, a pre-defined function from
Facebook's Java Script \ac{sdk} is called to perform the invitation.

\subsection{Data evaluation}
\label{sec:data-evaluation}
Data evaluation is performed by using the MySQL tables, and
PHP. In addition, the dot
language\footnote{http://www.graphviz.org/Documentation.php} is used
to create graphs.

@@

\section{Results}
\label{sec:results}
A total of n=48 users participated in the quiz. 5505 users have been
stored in the user table. Thus, on average each user brought on
average 114.7 \textit{new} people, who could read about the application
in their news stream. 15

@@

\begin{figure}
  \includegraphics[width=5.2in]{../img/allUserTree.png}
\caption{Figure shows all users stored in the database. Users who
  participated have a red text color.}
\label{fig:allUsers}
\end{figure}

In the following, only user who participated in the quiz are
considered. In Figure \ref{fig:spreading} nodes of people, who are
connector between two networks, have a red font color. The number of
friends and the average score from quiz are also shown. 
It can be obtained that in three cases, there are several connections (friendships)
between the people who participated and belong to a new network. For
instance, several connections exist between users \textit{Evan},
\textit{Diego}, \textit{Isabelle}, \textit{Chase}, and \textit{Gebrielle}.
\textit{Nicholas} and \textit{Chase}, who are friends with those
people mentioned above, also are friends with \textit{Ethan},
and \textit{Josiah}.  Then, \textit{Faith} is friend with
\textit{Owen} and \textit{Colton}, who also know each other, and
\textit{Mariah} and \textit{Sydney} have \textit{Alexis} as a common
friend. The figure also shows that most people who spread the
application had a score greater than or equal to three. At least, it
can be obtained that half of the people who spread the application
had less than hundred friends, which is less than the mean on
Facebook, i.e. 130 friends \cite{ref:facebookStats}.

@@

\begin{figure}
  \includegraphics[width=5in]{../img/spreading.png}
\caption{Figure shows all users stored in the database. Users who
  participated have a red text color.}
\label{fig:spreading}
\end{figure}

@@

\section{Discussion and Outlook}
\label{sec:discussion}
From the results given in section \ref{sec:results} it can be derived
that the number of friends did not to play a bigger role in the
process of the application's distribution. The number of connections
to other users seems to play a bigger 
role, as it is indicated by table \ref{tab:spread} and figure
\ref{fig:spreaders}. In addition, a worse score made people unlikely
to spread the application, just one person with a score less than 3
did so. Thus, people with a higher score (on average $3.11$, median $3.32$) are
supposed to have distributed the application. Indeed, some people who
had four or five friends who participated in the application did not
install the application.

In order to get more reliability towards the processes of distribution
of applications on Facebook, more applications must be analyzed.
Future research may consider, how patterns change with respect
to users' age, and if further characteristics can be identified. In
case of larger applications, it could be studied, if turning points
or intervals exist, which - when exceeded - make users significantly
more likely to join the application.

\section{Conclusion}
\label{sec:conclusion}
This research indicates, that the spreading of application follows
certain patterns. Oftentimes, people say that they don't want to
make a worse impression on Facebook, and this is also reflected in the
fact, that only people who yield higher scores in the quiz also
distributed to their friends. In the environment analyzed, dense
networks with few participants, i.e. in networks in which people know
each other, made  further members of their network very likely to join
the application. Indeed, the number of friends did not play a role in
making people likely to spread the application.

@@

\newpage
\section{Addendum}
\label{sec:addendum}
\begin{figure}
  \includegraphics[width=3.5in]{../img/fbsolution.png}
  \caption{Solution of a question.}
\label{fig:solution}
\end{figure}

\begin{figure}
  \includegraphics[width=3.5in]{../img/fbinvite.png}
  \caption{This screenshot shows how friends can be invited.}
\label{fig:invite}
\end{figure}

>>>>

%\usepackage[latin1]{inputenc} % Zeichencodierung
%\usepackage[T1]{fontenc} % Zeichencodierung

@@

\title{Spreading of a Facebook Application}

@@

\begin{abstract}
%% Text of abstract, 150 - 350 words
% The outcome was students' perceptions of preparedness.
Applications on Facebook are popular and attract many
people. Nevertheless, before installation people must acknowledge that an application
exists, and they must demand the application, too.
There may exist several reasons for people to install
applications, such as intensive usage within their social network, or
personal interest in a special topic. Persuasion can
happen virally through Facebook's news stream, by marketing through
friends, or by directed search on 
Facebook. Differences in the spreading process are supposed to exist
for the different kinds of applications.

This paper investigates, how a quiz asking people five randomly
selected questions about dentistry health facts spreads on
Facebook. The quiz is made social by providing participants with
information such as if they were better than their
friends and other users, and which of their friends could answer the given questions.

Analysis is supported by a tool maintaining an internal representation
of an extract of Facebook's social graph containing the participants
as nodes, their friendships as edges, and their basic information
retrieved from Facebook as well as quiz results as node
attributes. The tool allows for output of aspects of the internal graph
in DOT-language, and export of metrics to CSV, too.

Results show that participants, who connect the network of existing
users to a new one, often achieved a relatively high score in the quiz. New
participants often had strong connections to the network of people who
already participated. Indeed, the number of friends did not seem to make
users more or less likely to gather new participants for the quiz.
\end{abstract}

@@

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
Facebook, Spreading of Applications, Social Network, data mining, social graph
\end{keyword}

@@

\section{Introduction}
\label{sec:introduction}
Founded in 2004, Facebook\footnote{www.facebook.com} has
become a social network currently used by more than 600 million people
all over the world\cite{facebook500}. Since 2007, Facebook provides an API permitting
third party developers to embed their own applications in
Facebook\footnote{http://developers.facebook.com/blog/archive}.
Subsequent to the F8 conference in April, 2010, Facebook simplified
access to its social graph by allowing
external websites for integration in their social graph through Open
Graph Protocol\cite{facebookStats} .

Due to integration in Facebook's social graph, third party
applications not only spare user authentication procedures, but can also access
extracts of Facebook's social graph, too. These information provided
by Facebook detail a user's friend list, basic information, and
further data to which access has to be granted by access tokens
\footnote{http://developers.facebook.com/docs/authentication/}. Thus,
applications let Facebook's social graph enlarge and make people
spend more time of Facebook. In addition, application developers
can spread their application virally through appearance in news
streams, and collect useful information about the social network of
their users, too.

Statistics show development of Facebook applications being very
attractive nowadays. Until October, 2009, 
over 350 000 apps had been seen on Facebook \cite{facebookBlog}.
According to current statistics, about 20 million applications are
installed per day, and ten thousand new websites integrate with
Facebook every day, too. \cite{facebookStats}

This paper investigates the process of spreading of applications on
Facebook by focusing on the show case of a quiz asking users five randomly
selected questions about dentistry health facts. User data are
collected in a MySQL database, and evaluation of the data is
accomplished by the outputs of a tool maintaining an internal representation of the extract of Facebook's
social graph the application is allowed to access.

The tool allows for output of graphs in \ac{dot} language and output of
metrics as \ac{csv}. The graphs the tool can output detail how the application
spreads, and allows for labelling of people (nodes) which connect the
network of existing user to new networks. The metrics detail with how
many people users who participated are friends, which score they had,
and to how many new people they could have spread the application.

In the first section, basic information about Facebook's social graph,
and integration of applications is
given. In the next section, the methodology is described by detailing
the quiz and its building, as well as the tool for data evaluation. Section
\ref{sec:results} presents the results, and in section
\ref{sec:discussion} and \ref{sec:outlook}, a discussed follows. Section
\ref{sec:conclusion} concludes the paper by summing up the results,
and giving an outlook for further research, too.

\section{Foundations}
\label{sec:background}
This section details concepts from Facebook, basics about the
\ac{DOT} language, and at least, it defines the metrics the tool
explained in section \ref{sec:methodology} can output. Facebook's
social graph concept is explained in 
section \ref{sec:social-graph}, section \ref{sec:integr-appl-with}
describes how applications can be integrated with Facebook, and
section \ref{sec:auth-auth} makes clear how applications can be
integrated with Facebook.

\subsection{Social Graph}
\label{sec:social-graph}
Facebook's \textit{social graph} can be regarded as its core. It
represents connections between people and things people care about 
\cite{facebookDev}. Since April, 2010, Facebook allows for access to its
social graph via the Open Graph Protocol\footnote{http://ogp.me/}, thus facilitating
external websites and third party applications to integrate in the social graph by becoming
additional nodes\cite{facebookDev2}. These additional nodes can for
instance represent entities such as movies, news articles,
applications, and much more. People on Facebook can add connections
from their user node to these additional nodes by clicking on plugins
provided by Facebook such as \textit{Like Buttons} or entering content in \textit{Comment
  Boxes}.  \cite{facebookDev2} As images of friends who liked an
entity, and comments of friends can be shown on external websites via
iframes, aspects from a user's social network are brought to these
websites, and for this reason, Facebook is said to make the Internet social.

In general, additional nodes representing external websites are integrated
unidirectional. Thus, Facebook retrieves the information in which
entities users were interested in, while the external websites do not
gain access to Facebook's social graph. Instead, the social
information is included through iframes.
In order to integrate nodes bi-directional, the user must permit the
access, and both, the user, and the entity, which wants to gain access
to the social graph, must be authenticated. This process is detailed in
section \ref{sec:auth-auth}. This happens in case of applications on
Facebook, thus they are included bi-directional and can grab
information from Facebook's social graph.

The Graph API is one of Facebook's core concepts and presents a consistent
view of the social graph. Every object has an unique ID and if it is
public, its properties can be accessed by requesting the appropriate URL:
\url{https://graph.facebook.com/ID}. Listing \ref{list:kbecker} shows
the author's public user node on Facebook's social graph. which is
returned as a \ac{json}-object\footnote{http://www.json.org}.

@@

In order to get access not only to public, but also to private
information, an access token has to be included in the Graph API
request. To get this token, the accessing entity must be
authorized and authenticated to do so. How this can be achieved is
explained in section \ref{sec:auth-auth}. When trying to access
non-public information without the needed access token, an error
is returned. Listing \ref{list:kbeckerfriends} gives an example for this.

@@

Facebook provides several features to support the development
process. \ac{sdks} exist for popular programming languages and provide
sets of pre-defined functions for communication with Facebook. For
instance, they include the O-Auth 2.0 dialog which is described in
section \ref{sec:auth-auth}. In
addition, Facebook grants observation of its own development process by
making its raodmap public, and by showcasting its buglist. In addition, a
testserver exists to help developers to analyze if their application
is going to run with planned features from Facebook. 
Facebook provides an \textit{insights}-feature which makes
statistics about the applications available. \cite{oreilly}.

@@

\subsection{Software Metrics}
\label{sec:metrics}
Metrics define a mapping of a `particular measurable entity to a
numerical value' \cite{Lanz06a}. Thus, they allow for analysis and summarization
of properties which are oftentimes not measurable. In addition, they
facilitate detection of `outliers in large amounts of data'
\cite{Lanz06a}. Metrics can be plotted as diagrams or charts, or they
can be used for visualizations such as graphs connecting nodes
characterized by metrics. Since humans are trained in understanding signs and
pictures, visualizations supports understanding and identifying of
`hidden aspects'. \cite{Lanz06a} In this paper, they are
employed to characterize users of the quiz. Some metrics can be output
as \ac{pdf}, and others are used to create the graphs in \ac{dot} language.

The following metrics can be calculated:

\begin{itemize}
\item A user's number of friends.
\item A user's score.
\item The number of friends who also participated in the quiz.
\item The number of friends who used the application, and belong to a
new network, thus the only connector between the new users' nodes and
the other nodes of the graph is the node of the user analyzed.
\end{itemize}

\section{Methodology}
\label{sec:method}
This section describes the methodology. At first, the quiz which is
used to collect data from Facebook's social graph is described as well
as its implementation (section \ref{sec:quiz}).
Then, it is explained how data are collected for
further analysis and how they can be evaluated.

\subsection{The Analyzed Application}
\label{sec:quiz}
The application analyzed in this paper is a quiz. It is described in
\ref{sec:aboutQuiz}, and in \ref{sec:implmentation} its implementation
is detailed.

\subsubsection{About The Quiz}
\label{sec:aboutQuiz}
The quiz is about dental health fact and also challenging. It can be
found at the URL \url{http://apps.facebook.com/zahniquiz}.
Each participants is asked five questions randomly selected
from a set of twenty questions. A question has four answers, of
which either one, two, three or each answer can be correct, thus
the kind of answers refers to the term \textit{multiple selection}.
A question is scored to be answered correctly, if the correct subset
was selected by the user, thus each correct and no incorrect answer
were selected. Each question answered correctly scores one, thus the
highest score is five. Figure \ref{fig:quiz} gives a screenshot of the quiz.

The quiz is competitive. After the quiz is completed, users are told
their score, and in addition, they acknowledge how good they were in
comparison to other participants as well as to their 
friends. As shown in figure \ref{fig:solution}, for each question the
correct solution is given. A user can also invite friends to
participate. For this issue, profile pictures of a user's friends are
printed beyond the quiz. By clicking on such an image, an invitation
can be sent to the friend's Facebook profile.

\subsubsection{Implementation}
\label{sec:implementation}
The studied application makes use of 
Facebook's php-\ac{sdk} and JavaScript-\ac{sdk}\footnote{http://developers.facebook.com/docs/}. It requires
permissions (see \ref{sec:auth-auth}) for \textit{user$\_$birthday} and
\textit{publish$\_$stream}.
The questions and answers of the quiz are stored in a MySQL-database. PHP scripts
handle the creation of the quiz and
the Pear DB module \footnote{http://pear.php.net/} is used
for database queries.

The structure of the Facebook application is related to a
Model-view-controller architecture. \textit{Pear::DB} represents the
model, files stored in folder \textit{templates} act as view
(\textit{quizQuestion.php}, \textit{quiz.php},
\textit{quizResult.php}), and \textit{index.php} assumes the role of
the controller. \textit{library.php} contains a collection of
functions used by the various PHP scripts. \textit{facebook.php} and
scripts from \textit{facebook-sdk} folder are downloaded from
\url{https://github.com/facebook/php-sdk/} provide the functionality
of Facebook's PHP \ac{sdk}.

The view operates as follows: \textit{quiz.php} checks if the user
completed the quiz. If not, it prints the form, loads the styles and
includes \textit{quizQuestion.php} to print the questions. Otherwise, it
creates the page shown after the quiz is completed by printing a
statement commenting the user's score, and by providing users with 
the following options: Users can print their result into their news
stream and they can send invitations to their friends' Facebook
profiles. For both options, Facebook's JavaScript \ac{sdk} is
used. \textit{quizResult.php} contains the code to  
print the correct solution after the quiz is completed and is included
by \textit{quizQuestion.php}.

\paragraph{Database schema}
\label{sec:database-schema}
The database queries are performed with PHP
pear\footnote{http://pear.php.net/}-package. The following tables exist:
\begin{itemize}
\item \textbf{User} - entries are created for each user who participates as
well as for each of a user's friends. A flag details if user
participated or not.
\item \textbf{Friends} - creates entries for each friendship found in
users' friend lists.
\item \textbf{Questions} - contains the questions of the quiz.
\item \textbf{Answers} - contains the possible answers and a flag to mark them
as correct or false.
\item \textbf{GivenAnswers} - stores each answer given by a user.
\item \textbf{UserScore} - stores the score user had in the quiz.
\item \textbf{CorrectAnsweredQuestions} - stores which questions were correct
answered by which user, and which were not.
\end{itemize}

\paragraph{Application flow}
\label{sec:application-flow}
When a user accesses the canvas page of the quiz, 
the \textit{OAuth Dialog} is started automatically by the
\textit{controller}. If authorization and authentication are completed
successfully, the user's basic data as well as the birthday are stored together with
a timestamp in the \textit{User} table. Column \textit{has-used-app} is set to 1. In
addition, each user's friends list is also stored in \textup{User} and
\textit{Friends} table, and for these \textit{users}, columns
\textit{has-used-app} is set to 0.

% the quiz is created by randomly choosing
% five questions from the questions table and requiring the answers. To
% make the questions more attractive, the name of an image convenient to
% the questions topic is also stored in the questions table, and this
% image is placed on the left side of each question. Since multiple
% selection is possible, before the answers, which are also queried from
% the MySQL database, checkboxes are placed before each answer. 
Next, the quiz is created as mentioned in section
\ref{sec:implmenetation}.
After completion, its is evaluated the final score is computed. As
each answer ought to be stored and multiple selection of answers is
possible, user answers have to be stored in  a multidimensional.

The given answers are then stored in table \textit{GivenAnswers}. In
table (\textit{correctAnsweredQuestions)} it is stored which questions
were correct or incorrect answered. This happens to spare complicated
evaluations based on the \textit{GivenAnswers} table later on.
Finally, an average score is computed and stored in the user table.

% In order to make the whole thing challenging, it
% is then computed how high the user's score is compared to the friends
% and to all the other users. 
% In addition, the correct solutions are given, and if a user knew the
% right answer, a green check is placed left to the question. Otherwise,
% a red cross is displayed at the same place. At least, the table with
% the friendships and table \textit{correctAnsweredQuestions} are used
% to identify friends  which answered the question correctly. Images of
% them are placed beyond each question's solution together with the
% information that those friends knew the right solution. 
% In the end, users get the chance to invite friends to the app to
% challenge them. For this reason, each friend's picture is added and
% user can click at them. On click, a pre-defined function from
% Facebook's Java Script \ac{sdk} is called to perform the invitation.

\subsection{Data evaluation}
\label{sec:data-evaluation}
Data evaluation is performed by using the MySQL database, and
PHP scripts. In addition, the dot
language\footnote{http://www.graphviz.org/Documentation.php} is employed
to create graphs.

@@

\section{Results}
\label{sec:results}
A total of n=52 users participated in the quiz. 6311 users have been
stored in the user table. Thus, on average each user brought on
average 121.4 \textit{new} people, who could read about the application
in their news stream.

@@

\begin{figure}
  \includegraphics[width=5.2in]{../img/tree2.png}
\caption{Figure shows all users stored in the database. Users who
  participated have a red text color.}
\label{fig:allUsers}
\end{figure}

In the following, only user who participated in the quiz are
considered. In Figure \ref{fig:spreading} nodes of people, who are
connector between two networks, have a red font color. The number of
friends and the average score from quiz are also shown. 
It can be obtained that in three cases, there are several connections (friendships)
between the people who participated and belong to a new network. For
instance, several connections exist between users \textit{Evan},
\textit{Diego}, \textit{Isabelle}, \textit{Chase}, and \textit{Gebrielle}.
\textit{Nicholas} and \textit{Chase}, who are friends with those
people mentioned above, also are friends with \textit{Ethan},
and \textit{Josiah}.  Then, \textit{Faith} is friend with
\textit{Owen} and \textit{Colton}, who also know each other, and
\textit{Mariah} and \textit{Sydney} have \textit{Alexis} as a common
friend. The figure also shows that most people who spread the
application had a score greater than or equal to three. At least, it
can be obtained that half of the people who spread the application
had less than hundred friends, which is less than the mean on
Facebook, i.e. 130 friends \cite{facebookStats}.

@@

\begin{figure}
  \includegraphics[width=5in]{../img/spreading5.png}
\caption{Figure shows all users stored in the database. Users who
  participated have a red text color.}
\label{fig:spreading}
\end{figure}

@@

\section{Discussion}
\label{sec:discussion}
From the results given in section \ref{sec:results} it can be derived
that the number of friends did not to play a bigger role in the
process of the application's distribution. The number of connections
to other users seems to play a bigger 
role, as it is indicated by table \ref{tab:spread} and figure
\ref{fig:spreaders}. In addition, a worse score made people unlikely
to spread the application, just one person with a score less than 3
did so. Thus, people with a higher score (on average $3.11$, median $3.32$) are
supposed to have distributed the application. Indeed, some people who
had four or five friends who participated in the application did not
install the application.

\section{Conclusion and Outlook}
\label{sec:conclusion}
This research indicates, that the spreading of application follows
certain patterns. Oftentimes, people say that they don't want to
make a worse impression on Facebook, and this is also reflected in the
fact, that only people who yield higher scores in the quiz also
distributed to their friends. In the environment analyzed, dense
networks with few participants, i.e. in networks in which people know
each other, made  further members of their network very likely to join
the application. Indeed, the number of friends did not play a role in
making people likely to spread the application.

In order to get more reliability towards the processes of spreading
of applications on Facebook, more applications must be analyzed.
Future research may consider, how patterns change with respect
to users' age, and if further characteristics can be identified. In
case of larger applications, it could be studied, if turning points
or intervals exist, which - when exceeded - make users significantly
more likely to join the application.

@@

\newpage
\section{Addendum}
\label{sec:addendum}

\begin{figure}
  \includegraphics[width=3.5in]{../img/fbsolution.png}
  \caption{Solution of a question.}
\label{fig:solution}
\end{figure}

% \begin{figure}
%   \includegraphics[width=3.5in]{../img/fbinvite.png}
%   \caption{This screenshot shows how friends can be invited.}
% \label{fig:invite}
% \end{figure}
